AD Target Gene Report

### 2020-01-21 code/02-Master.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
```

@@

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}

```{r Module1, eval = T, include=T}
if( i %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source()

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
opts_knit$set(root.dir = '../')
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
#webshot::install_phantomjs()
```

@@

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA

for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
```

```{r Module1, eval = T, include=T}
if( 1 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source('code/modules/01-IGAP_module.R')

@@

```{r Module2, eval = T, include=T}
if( 2 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence')

  source('modules/02-DiffExp_module.R')

}else{
  writeLines('Skipping Differential Expression based Model and Gene-Ranking: User specified module 2 not included in <Config>.yaml ')
}

### 2020-01-21 code/03-Run.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
```

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(configuration)

@@

```{r Process, eval=T, include=T}

  writeLines('Importing genelist ', config$genelistfile, ' as ', config$Genelisttype)

```{r GeneNames, eval=T, include=T}
GeneData <- function( id ){

  org = 'hsa'
  id.type = 'ensembl_gene_id'
  #host = 'jul2019.archive.ensembl.org'
  host = 'grch37.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

  ensembl <- useDataset(ds, mart = ensembl)

  Genes <- getBM(filters = id.type, attributes = c(id.type, 'hgnc_symbol', 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
  return(Genes)
}

Tab <- GeneData( Genes )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}

```
```{r Module1, eval = T, include=T}
if( i %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
opts_knit$set(root.dir = '../')
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
#webshot::install_phantomjs()
```

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(file=paste0(configuration))

@@

Importing genelist `r thisFile` as `r config$genelisttype`
```{r GeneNames, eval=T, include=T}

GeneData <- function( id, type ){
  #Retreives gene name info
  #'@id the gene ids to source a list from
  #'@type either ENSG or GNAME for type of gen ids

  org = 'hsa'
  host = 'grch37.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

  if(type == 'ENSG'){
    id.type = 'ensembl_gene_id'
    ensembl <- useDataset(ds, mart = ensembl)
    Genes <- getBM(filters = id.type, attributes = c(id.type, 'hgnc_symbol', 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
  }else{
    if(type == 'GNAME'){
      id.type = 'hgnc_symbol'
      ensembl <- useDataset(ds, mart = ensembl)
      Genes <- getBM(filters = id.type, attributes = c('ensembl_gene_id', id.type, 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
      ##Cut Decmals
    }else{
      #Error Gene names not specififed correctly
      stop("ERROR: SOURCE=Config.yaml Issue=genelisttype must be ENSG or GNAME")
    }
  }
  return(Genes)
}

#Load Gene Set:
Genes <- read.table( paste0(config$filedir, '/genelists/', config$genelistfile ), header=F, sep='\t')

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
```

```{r Module1, eval = T, include=T}
if( 1 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source('code/modules/01-IGAP_module.R')
